`r title`

### 2017-12-12 lib/report.Rmd
progress

Citation issued: `r citation_issued_pct`

Arrest made: `r arrest_made_pct`

```{r plot_props_by_race}
search_conducted_by_race_plot
contraband_found_by_race_plot
citation_issued_by_race_plot
arrest_made_by_race_plot
```

>>>>

```{r plot_props_by_race}
search_conducted_by_race_plot
contraband_found_by_race_plot
```

```{r outcome_by_race_plot, fig.height = 10}
outcome_by_race_plot
```
